
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End: 
\documentclass[twocolumn]{article}

% Packages
% \usepackage{fancyhdr}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[margin=10mm]{geometry}
\usepackage{graphicx}



% Housekeeping
\pagestyle{empty}

\begin{document}

\begin{itemize}
\item Embedded system benefits: economy, efficiency, geographical
  separation, flexibility, reliability, scalability.
\item Embedded system challenges: 
\item Definition for a computer system, in the process scale.
  \begin{itemize}
  \item Minimal unit of an autonomous computer system, an instance of
    computer program execution.
  \item Independent computational resource access.
  \item Processes can communicate with other within the same machine,
    or across different machines (over a communication network). 
  \end{itemize}
\item Thread may not have independent access to computational
  resources. 
\item Middleware provides transparency to hardware resources.
\item Examples of distributed objects are: CORBA, DCOM, Java RMI\@.
\item For messaging/event based communication, the explicitly timeout
  mechanism is required.
\item Networks of Computers. 
  \begin{itemize}
  \item Network core: Interconnected global ISPs. Well connected
    topology. High bandwidth capacity.
  \item Network edge. Local ISPs. Local networks in homes,
    institutes. And\ldots mobile networks. Something about the
    last-mile congestion.
  \end{itemize}
\item Virtualization broadly refers to abstraction of resources in
  many aspects of computing. Concepts are: Hypervisor, Hardware
  virtualization, Software virtualization.
\item Virtualization can reduce operation costs by consolidating
  services to fewer number of physical machines.
\item Application of overlay networks are: robust networking,
  multicasting, and VoIP\@.
\item Consistency ensures: Transparency among distributed processes
  and Correctness of data transactions spanning multiple databases.
\item To guarantee consistency among distributed processes, it is
  necessary to provide mutual exclusion when accessing a critical
  section. For mutual exclusion, there are several types of algorithms,
  centralized, distributed, or token ring.
\item Problems for these types of algorithms: centralized, coordinator
  crash; distributed, process crash; token ring, lost token and
  process crash.
% \item Life is hard but you have to get used to it. Victory or death,
%   choose one. I choose not to be killed.
\item Transactions. We consider processes accessing multiple disparate
  databases. A transaction is an agreement between separate entities
  or objects, often involving the exchange of items of value.
\item Properties of transactions:
  ACID\@. Atomic. Consistent. Isolated. Durable. 
\item Three-Phase Commit: add time-out into two-phase then we could
  abort prevent locking resource.
\item Hiding failure from other processes using redundancy: time
  redundancy, physical redundancy and information redundancy.
\item Recovery tries to correct errors due to faults. They could be
  divided into two types: backward and forward.
  \begin{itemize}
  \item Backward: checkpointing, retransmit lost packages.
  \item Forward: error=correction codes.
  \end{itemize}
\item Challenges for wireless communication: noise, shared
  communication medium, limited spectrum, mobility, energy
  efficiency.
\item  

\end{itemize}

\end{document}
